Turbulence and Particle Acceleration in Giant Radio Halos: the Origin of Seed Electrons

### 2016-05-06 paper.tex
restructuring paper, editing dummy's guide

\renewcommand{\vec}{\ensuremath{\mathbfit}}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\Vph}{V_\mathrm{ph}}
\newcommand{\mug}{\umu G}
\newcommand{\RH}{R_\rmn{RH}}
\newcommand{\bvel}{\ensuremath{\boldsymbol{\varv}}}
\newcommand{\bnabla}{\ensuremath{\boldsymbol{\nabla}}}
\newcommand\eb{\epsilon_\rmn{B}}
\newcommand{\dps}{\displaystyle}
\newcommand{\p}{\rmn{p}}
\newcommand{\kB}{k_{\rmn{B}}}
\newcommand{\eps}{\varepsilon}

@@

\begin{figure}
  \includegraphics[width=1.0\columnwidth]{fCR.radius.coma.g72a.Rad14.2400p.z0.NL.xKR.eb23.eI067.DII.140.v6.eps}
  \caption{Spatial distribution of CRp energy density in the Coma
    cluster. The red dash-dotted line shows the required distribution
    of seed CRps that generate secondary electrons via p-p collisions
    required to reproduce Coma radio brightness observations after
    Fermi-II reacceleration \citep{brunetti12}. The blue solid line
    shows the distribution of fossil CRps found in cosmological
    simulations, which disagrees with the required profile. To better
    compare the two models in this figure, we normalize the required
    distribution of CRps by fixing the total CRp energy $E_\rmn{CR}$
    to 0.3 percent of the total thermal energy, consistent with
    observations \citep{2014ApJ...787...18A,2012ApJ...757..123A}.}
  \label{fig:Edens}
\end{figure}

@@

% --- section: Method --- %
\section{Method}

@@

\SPO{explain overall picture, $\tau_\rmn{d}$ vs. $\tau_{\rmn{cl}}$}

\subsection{Cosmic ray transport}
As previously noted, secondaries produced by shock accelerated CRp
have the wrong spatial profile to explain RH observations. Because
they arise from a two body process, they are too centrally
concentrated. They also produce $\gamma$-ray emission in excess of
Fermi-LAT upper limits
\citep{2012ApJ...757..123A,brunetti12,2014ApJ...787...18A}. However,
if CRps stream in the ICM, then their spatial profile could
potentially flatten sufficiently \citep{ensslin11,wiener13}. This
scenario is very attractive: it generates seed electrons with the
right spatial footprint, and by removing CRps from the core, obeys
gamma-ray constraints. Turbulence plays two opposing roles:
Alfv{\'e}nic turbulence damps waves generated by the CR streaming
instability \citep{yan02,farmer04}, thus reducing self-confinement;
but compressible fast modes scatter CRs directly. Turbulent damping is
still efficient for highly subsonic conditions \citep{wiener13}, while
we assume compressible fast modes to only provide effective spatial
confinement during the periods of transonic, highly super-Alfv{\'e}nic
($M_{\rm A} \sim 5$) turbulence associated with mergers. Thus, CRs can
stream out when the cluster is kinematically quiescent. Furthermore,
even Alfv{\'e}nic streaming timescales are relatively short
\cite[$\sim 0.1-0.5$ Gyr;][]{wiener13} compared to the timescale on
which the CRp population is built up. Based on these findings, we
adopt a toy model for our \Mstream scenario in which CR streaming
instantaneously produces flat CRp profiles.

Given a seed population of CRs, we adopt essentially the same set of
plasma physics assumptions as the reacceleration model for RHs
\citep{brunetti07,brunetti11}. We solve the isotropic, gyro-phase
averaged Fokker-Planck equation (via a Crank-Nicholson scheme) for the
time evolution of the CRe distribution in the Lagrangian frame
\citep{brunetti07,brunetti11}:
\begin{eqnarray}
{{d f_{\rmn{e}}(p,t)}\over{d t}} &\!=&
\frac{\partial}{\partial p}
\left\{
f_{\rmn{e}}(p,t)\left[
\left|\frac{dp}{dt}\right|_{\rm Coul} 
+ \frac{p}{3}\left(\bnabla\bcdot \bvel\right)
+ \left|\frac{dp}{dt}\right|_{\rm rad}\right.\right.
\nonumber\\
&-& \left.\left.{1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right) 
\right]\right\} - \left(\bnabla\bcdot \bvel\right) f_{\rmn{e}}(p,t)
\nonumber\\
&+& {{\partial^2 }\over{\partial p^2}}
\left[
D_{pp} f_{\rmn{e}}(p,t) \right]+ Q_{\rmn{e}}\left[p,t;f_{\rmn{p}}(p,t)\right]   \, .
\label{elettroni}
\end{eqnarray}
Here $f_{\rmn{e}}$ is the one-dimensional distribution in position $x$
(suppressed for clarity), momentum $p$ and time $t$ (which is
normalized such that the number density is given by
$n_{\rmn{e}}(t)=\int d p f_{\rmn{e}}(p,t)$), $d/dt=\partial/\partial
t+\bvel\bcdot\bnabla$ is the Lagrangian derivative, $\bvel$ is the gas
velocity, $|dp/dt|$ represents radiative
\citep[rad,][]{1979rpa..book.....R} and Coulomb
\citep[Coul,][]{1972Phy....60..145G} losses, \AP{please insert
  formulae: -- done}
\begin{eqnarray}
   \left|\frac{dp}{dt}\right|_{\rm Coul} &=& \frac{3\,\sigma_\rmn{T}\,n_e\,c}{2\, \beta^2}
  \left[\ln\left(\frac{m_e c^2 \beta \sqrt{\gamma-1}}{\hbar\,\omega_\rmn{plasma}}\right)\right.\nonumber \\
    &-&\ln(2)\left(\frac{\beta^2}{2}+\frac{1}{\gamma}\right)+\frac{1}{2}+
    \left.\left(\frac{\gamma-1}{4\gamma}\right)^2\right]\,, \\
  \rmn{where} &\,& \beta = p/\sqrt{1+p^2}\,,\qquad \gamma=\sqrt{1+p^2}\,, \quad\rmn{and}\nonumber \\
  \left|\frac{dp}{dt}\right|_{\rm rad~} &=& \frac{4}{3}\frac{\sigma_\rmn{T}}{m_ec}\,
  \frac{p^2}{\beta}\,\left[1+\left(\frac{B}{B_\rmn{CMB}}\right)^2\right]\,.
\end{eqnarray}
Here $\omega_\rmn{plasma} = \sqrt{4\pi e^2 n_e / m_e}$ is the plasma
frequency, $n_e$ is the number density of free electrons, and
$\sigma_\rmn{T}= 8\pi e^4/3(m_e c^2)^2$ is the Thomson cross
section. The {\it rms} magnetic field strength is denoted by $B$ and
the equivalent field strength of the cosmic-microwave background is
given by $B_\rmn{CMB} = 3.24 (1 + z)^2\mu\rmn{G}$, where $z$ denotes
the redshift. In the peripheral cluster regions, where $B <<
B_\rmn{CMB}$, the CRes loose virtually all their energy by means of
inverse Compton emission. $D_{pp}$ is the momentum space diffusion
coefficient (see Sect.~\ref{sec:reacc}), and $Q_{\rmn{e}}$ denotes the
injection rate of primary and secondary electrons in the ICM (see
Sect.~\ref{sec:cosmo_sim}). The first term containing the expression
$\bnabla\bcdot \bvel$ represents Fermi-I acceleration and the second
term of this form describes adiabatic gains and losses.

@@

The time evolution of the spectral energy distribution of CRps,
$f_{\rmn{p}}$, is similarly given by:
\begin{eqnarray}
\lefteqn{
  {{d f_{\rmn{p}}(p,t)}\over{d t}} =
  {{\partial }\over{\partial p}}
  \left\{
  f_{\rmn{p}}(p,t)\left[ \left|{{dp}\over{dt}}\right|_{\rm Coul}
    + \frac{p}{3}\bnabla\bcdot \left(\bvel+\bvel_{\rmn{st}}\right)\right.\right.}
\nonumber\\
&&-\left.\left. {1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right)
\right]\right\} - f_{\rmn{p}}(p,t) \bnabla\bcdot \left(\bvel+\bvel_{\rmn{st}}\right) 
- \bvel_{\rmn{st}}\bcdot\bnabla f_{\rmn{p}}(p,t)
\nonumber\\
&&+\,\,\, {{\partial^2 }\over{\partial p^2}}
\left[ D_{pp} f_{\rmn{p}}(p,t) \right] - {{f_{\rmn{p}}(p,t)}\over{\tau_{\rm had}(p)}}
+ Q_{\rmn{p}}(p,t)\, ,
\label{eq:FP_p}
\end{eqnarray}
where $\bvel_{\rmn{st}}=-\varv_{\rmn{A}}\bnabla f_{\rmn{p}}/|\bnabla
f_{\rmn{p}}|$ is the streaming velocity in the isotropic transport
approximation, $\varv_{\rmn{A}}$ is the Alfv\'en speed,
and $Q_{\rmn{p}}(p,t)$ denotes the injection rate of shock accelerated
CRps as a function of momentum $p$ and time $t$ (see
Sect.~\ref{sec:cosmo_sim}). The timescale of
hadronic losses that produce pions via CRp collisions with thermal
protons of the ICM is given by 
\AP{please insert formulae: -- done}
\begin{eqnarray}
  \tau_{\rm had} = \frac{1}{c\,n_\rmn{th}\,\sigma^{+/-,0}(p)}\,
\end{eqnarray}
where we use the cross-section, $\sigma^{+/-,0}(p)$, given by the
fitting formula in \citep{1986ApJ...307...47D}.

\subsection{Turbulent reacceleration}
\label{sec:reacc}

We incorporate momentum diffusion for electrons and protons via the
transit-time-damping (TTD) resonance with compressible MHD turbulence,
to model Fermi-II reacceleration \citep{brunetti07,brunetti11}. The
TTD resonance requires the wave frequency to obey the resonance
condition, $\omega=k_\parallel\varv_\parallel$, where $k_\parallel$
and $\varv_\parallel$ are the parallel (projected along the magnetic
field) wavenumber and particle velocity, respectively. This implies
that the particle transit time across the confining wave region
matches the wave period,
$\lambda_{\parallel}/v_{\parallel}=\tau_{\rmn{wave}}$. Note, the CRs'
gyroradius does not enter the resonance condition. Hence the CRs that
are in resonance with compressible waves experience Fermi-II
acceleration irrespectively of the length scale of the perturbation.

@@

The profile of injected turbulence depends on the details of the
merger such as time during the merger, the impact parameter, the
merger mass ratio, and the degree of cluster anisotropy
\citep{2015ApJ...800...60M}. We parametrize these uncertainties and
assume that it scales with the thermal energy density to some
power. Hence we assume volumetric injection rate of turbulent energy,
$I_0\propto \eps_\rmn{th}^{\alpha_\rmn{tu}}$, and determine the
normalization by requiring that the turbulent energy in compressible
modes $E_\rmn{turb}=\int \int \mathcal{W}(k) \rmn{d}k \rmn{d}V =
X_\rmn{tu} E_\rmn{th}$, where $E_\rmn{th}$ is the total thermal
energy. We adopt a turbulent energy ratio $X_\rmn{tu}=0.2$ within the
radio halo.\footnote{Simulations show that the compressible modes
  contribute a factor $0.2-0.4$ to the total turbulent energy
  \citep{2013ApJ...771..131B,2015ApJ...800...60M}. Furthermore, the
  total turbulent energy, which can be decomposed into a slenoidal and
  compressible component, is typically $\sim15-70$\% of the thermal
  energy in a cluster \citep{2011A&A...529A..17V}; in agreement with
  our adopted value of $X_\rmn{tu}$.} In this work we investigate
different spatial models for injected turbulence. With the above
choice of normalization, the turbulent energy density becomes
$\eps_\rmn{turb} \propto
\eps_\rmn{th}^{(\alpha_\rmn{tu}+1)/2}/T^{1/4}$, where $T$ is the
temperature of the gas, $\alpha_\rmn{tu}= 0.67$ for \Mflatturb,
$\alpha_\rmn{tu}= 0.82$ for \Mstream, and $\alpha_\rmn{tu}= 0.88$ for
\Mprimary (see Figure~\ref{fig:turb} for visualization). \CP{These
  models and scaling indices are not well motivated here, they would
  better fit into the results section.}

Note that in previous work on the Coma cluster, $\eps_\rmn{turb}
\propto \eps_\rmn{th}$ was adopted which roughly corresponds to
$\alpha_\rmn{tu}= 1$ \citep{brunetti12} and together with the
different distributions for seed CRes constitute the main differences
compared to our work. Our flatter turbulent profiles are motivated by
fits to cosmological simulations
\citep{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V,2012ApJ...758...74B}
and the range indicates uncertainties of the turbulent profile in
Coma. Future observations (by Astro-H) and simulations will help to
clarify this issue. Provided dissipation of turbulence in the ICM is
collisionless, turbulent cascades of compressible modes become
suppressed when thermal and relativistic particles resonantly interact
with magnetosonic waves via TTD on a timescale $\Gamma^{-1}$ that
approaches the cascading timescale given by $\tau_{kk} \approx
k^2/D_{kk}$. Thus, the cascade is suppressed for wave numbers above
\begin{equation}
\label{eq:kc}
  k_\rmn{cut} \approx \frac{81}{14} \frac{I_0}{\rho \langle \Vph \rangle}
  \left(\frac{\langle\sum_i \Gamma_i(k,\theta)\rangle}{k}\right)^{-2}\,,
\end{equation}
where $2\upi/k_\rmn{cut}\sim 0.1-1$~kpc in the ICM. This constitutes an
effective mean free path for CRs, unless plasma instabilities can
mediate interactions between turbulence and particles on smaller
scales \citep{brunetti11}.

>>>>

\renewcommand{\vec}{\ensuremath{\mathbfit}}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\Vph}{\varv_\mathrm{ph}}
\newcommand{\mug}{\umu G}
\newcommand{\RH}{R_\rmn{RH}}
\newcommand{\bvel}{\ensuremath{\boldsymbol{\varv}}}
\newcommand{\bnabla}{\ensuremath{\boldsymbol{\nabla}}}
\newcommand\eb{\epsilon_\rmn{B}}
\newcommand{\dps}{\displaystyle}
\newcommand{\p}{\rmn{p}}
\newcommand{\kB}{k_{\rmn{B}}}
\newcommand{\eps}{\varepsilon}

@@

\begin{figure}
  \includegraphics[width=1.0\columnwidth]{fCR.radius.coma.g72a.Rad14.2400p.z0.NL.xKR.eb23.eI067.DII.140.v6.eps}
  \caption{Spatial distribution of CRp energy density in the Coma
    cluster. The red dash-dotted line shows the required distribution
    of seed CRps that generate secondary electrons via proton-proton
    (p-p) collisions required to reproduce Coma radio brightness
    observations after Fermi-II reacceleration \citep{brunetti12}. The
    blue solid line shows the distribution of fossil CRps found in
    cosmological simulations, which disagrees with the required
    profile. To better compare the two models in this figure, we
    normalize the required distribution of CRps by fixing the total
    CRp energy $E_\rmn{CR}$ to 0.3 percent of the total thermal
    energy, consistent with observations
    \citep{2014ApJ...787...18A,2012ApJ...757..123A}.}
  \label{fig:Edens}
\end{figure}

@@

% --- section: Method --- %
\section{Cosmic ray transport}

@@

\subsection{Basic equations}
As previously noted, secondaries produced by shock accelerated CRp
have the wrong spatial profile to explain RH observations. Because
they arise from a two body process, they are too centrally
concentrated. They also produce $\gamma$-ray emission in excess of
Fermi-LAT upper limits
\citep{2012ApJ...757..123A,brunetti12,2014ApJ...787...18A}. However,
if CRps stream in the ICM, then their spatial profile could
potentially flatten sufficiently \citep{ensslin11,wiener13}. This
scenario is very attractive: it generates seed electrons with the
right spatial footprint, and by removing CRps from the core, obeys
gamma-ray constraints. Turbulence plays two opposing roles:
Alfv{\'e}nic turbulence damps waves generated by the CR streaming
instability \citep{yan02,farmer04}, thus reducing self-confinement;
but compressible fast modes scatter CRs directly. Turbulent damping is
still efficient for highly subsonic conditions \citep{wiener13}, while
we assume compressible fast modes to only provide effective spatial
confinement during the periods of transonic, highly super-Alfv{\'e}nic
($M_{\rm A} \sim 5$) turbulence associated with mergers. Thus, CRs can
stream out when the cluster is kinematically quiescent. Furthermore,
even Alfv{\'e}nic streaming timescales are relatively short
\cite[$\sim 0.1-0.5$ Gyr;][]{wiener13} compared to the timescale on
which the CRp population is built up. Based on these findings, we
adopt a toy model for our \Mstream scenario in which CR streaming
instantaneously produces flat CRp profiles.

Given a seed population of CRs, we adopt essentially the same set of
plasma physics assumptions as the reacceleration model for RHs
\citep{brunetti07,brunetti11}. We solve the isotropic, gyro-phase
averaged Fokker-Planck equation (via a Crank-Nicholson scheme) for the
time evolution of the CRe distribution in the Lagrangian frame
\citep{brunetti07,brunetti11}:
\begin{eqnarray}
{{d f_{\rmn{e}}(p,t)}\over{d t}} &\!=&
\frac{\partial}{\partial p}
\left\{
f_{\rmn{e}}(p,t)\left[
\left|\frac{dp}{dt}\right|_{\rm Coul} 
+ \frac{p}{3}\left(\bnabla\bcdot \bvel\right)
+ \left|\frac{dp}{dt}\right|_{\rm rad}\right.\right.
\nonumber\\
&-& \left.\left.{1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right) 
\right]\right\} - \left(\bnabla\bcdot \bvel\right) f_{\rmn{e}}(p,t)
\nonumber\\
&+& {{\partial^2 }\over{\partial p^2}}
\left[
D_{pp} f_{\rmn{e}}(p,t) \right]+ Q_{\rmn{e}}\left[p,t;f_{\rmn{p}}(p,t)\right]   \, .
\label{elettroni}
\end{eqnarray}
Here $f_{\rmn{e}}$ is the one-dimensional distribution in position $x$
(suppressed for clarity), momentum $p$ and time $t$ (which is
normalized such that the number density is given by
$n_{\rmn{e}}(t)=\int d p f_{\rmn{e}}(p,t)$), $d/dt=\partial/\partial
t+\bvel\bcdot\bnabla$ is the Lagrangian derivative, $\bvel$ is the gas
velocity, $|dp/dt|$ represents Coulomb
\citep[Coul,][]{1972Phy....60..145G} and radiative
\citep[rad,][]{1979rpa..book.....R} losses, respectively,
\begin{eqnarray}
   \left|\frac{dp}{dt}\right|_{\rm Coul} &=& \frac{3\,\sigma_\rmn{T}\,n_e\,c}{2\, \beta^2}
  \left[\ln\left(\frac{m_e c^2 \beta \sqrt{\gamma-1}}{\hbar\,\omega_\rmn{plasma}}\right)\right.\nonumber \\
    &-&\ln(2)\left(\frac{\beta^2}{2}+\frac{1}{\gamma}\right)+\frac{1}{2}+
    \left.\left(\frac{\gamma-1}{4\gamma}\right)^2\right]\,, \\
  \left|\frac{dp}{dt}\right|_{\rm rad~} &=& \frac{4}{3}\frac{\sigma_\rmn{T}}{m_ec}\,
  \frac{p^2}{\beta}\,\left[1+\left(\frac{B}{B_\rmn{CMB}}\right)^2\right]\,.
\end{eqnarray}
Here $\beta = p/\sqrt{1+p^2}$ is the dimensionless velocity of CRs,
$\gamma=\sqrt{1+p^2}$ is the Lorentz factor of CRs,
$\omega_\rmn{plasma} = \sqrt{4\pi e^2 n_e / m_e}$ is the plasma
frequency, $n_e$ is the number density of free electrons, and
$\sigma_\rmn{T}= 8\pi e^4/3(m_e c^2)^2$ is the Thomson cross
section. The {\it rms} magnetic field strength is denoted by $B$ and
the equivalent field strength of the cosmic-microwave background is
given by $B_\rmn{CMB} = 3.24 (1 + z)^2\mu\rmn{G}$, where $z$ denotes
the redshift. In the peripheral cluster regions, where $B \ll
B_\rmn{CMB}$, the CRes loose virtually all their energy by means of
inverse Compton emission. $D_{pp}$ is the momentum space diffusion
coefficient (see Sects.~\ref{sec:dummy} and \ref{sec:reacc}), and
$Q_{\rmn{e}}$ denotes the injection rate of primary and secondary
electrons in the ICM (see Sect.~\ref{sec:cosmo_sim}). The first term
containing the expression $\bnabla\bcdot \bvel$ represents Fermi-I
acceleration and the second term of this form describes adiabatic
gains and losses.

@@

The time evolution of the spectral energy distribution of CRps,
$f_{\rmn{p}}$, is similarly given by:
\begin{eqnarray}
\lefteqn{
  {{d f_{\rmn{p}}(p,t)}\over{d t}} =
  {{\partial }\over{\partial p}}
  \left\{
  f_{\rmn{p}}(p,t)\left[ \left|{{dp}\over{dt}}\right|_{\rm Coul}
    + \frac{p}{3}\bnabla\bcdot \left(\bvel+\bvel_{\rmn{st}}\right)\right.\right.}
\nonumber\\
&&-\left.\left. {1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right)
\right]\right\} - f_{\rmn{p}}(p,t) \bnabla\bcdot \left(\bvel+\bvel_{\rmn{st}}\right) 
- \bvel_{\rmn{st}}\bcdot\bnabla f_{\rmn{p}}(p,t)
\nonumber\\
&&+\,\,\, {{\partial^2 }\over{\partial p^2}}
\left[ D_{pp} f_{\rmn{p}}(p,t) \right] - {{f_{\rmn{p}}(p,t)}\over{\tau_{\rm had}(p)}}
+ Q_{\rmn{p}}(p,t)\, ,
\label{eq:FP_p}
\end{eqnarray}
where $\bvel_{\rmn{st}}=-\varv_{\rmn{A}}\bnabla f_{\rmn{p}}/|\bnabla
f_{\rmn{p}}|$ is the streaming velocity in the isotropic transport
approximation, $\varv_{\rmn{A}}$ is the Alfv\'en speed,
and $Q_{\rmn{p}}(p,t)$ denotes the injection rate of shock accelerated
CRps as a function of momentum $p$ and time $t$ (see
Sect.~\ref{sec:cosmo_sim}). The timescale of
hadronic losses that produce pions via CRp collisions with thermal
protons of the ICM is given by 
\begin{eqnarray}
  \tau_{\rm had} = \left[c\,n_\rmn{th}\,\sigma^{+/-,0}(p)\right]^{-1}\,,
\end{eqnarray}
where we use the cross-section, $\sigma^{+/-,0}(p)$, given by the
fitting formula in \citep{1986ApJ...307...47D}.

\subsection{Dummy's guide} 
\label{sec:dummy}

All of the physics of turbulent reacceleration is effectively encapsulated in the diffusion coefficient, which can be rewritten as \citep{2015ApJ...800...60M}:
\begin{equation}
D_{pp}(p) = \frac{ p^{2} \pi I_{\theta}(c_{s}/c)}{8 c} \langle k \rangle_{\mathcal{W}} \langle (\delta v_{\rm c})^{2} \rangle
\label{eqn:diffusion}
\end{equation}
\SPO{define $I_{\theta}(c_{s}/c)$ or explain its meaning in words and point to the definition provided in the next subsection.}
where
\begin{equation}
\langle k \rangle_{\mathcal{W}} = \frac{1}{\langle (\delta \varv_{\rm c})^{2} \rangle} \int_{k_{\rm L}}^{k_{\rm cut}} dk \, k \, \mathcal{W}(k) \approx \frac{s-1}{2-s} k_{\rm L} \left( \frac{k_{\rm cut}}{k_{\rm L}} \right)^{2-s} 
\end{equation}
is an energy-averaged wavenumber, $k_{\rm L}, k_{\rm cut}$ are the wavenumbers associated with the outer scale and the cutoff scale respectively, and we have assumed a total energy spectrum (both kinetic and potential energy, where the two are assumed to be in equipartition \citep{sarkar11}): 
\begin{equation}
\mathcal{W}(k) = \frac{(s-1) \langle (\delta \varv_{\rm c})^{2} \rangle}{k_{\rm L}} \left( \frac{k}{k_{\rm L}} \right)^{-s} 
\label{eqn:Wk}
\end{equation}
which defines the normalization $\langle (\delta \varv_{\rm c})^{2} \rangle$ (the subscript 'c' emphasizes that we specialize to compressive modes). Intuitively, we can understand the form of the the diffusion coefficient from the fact that for second-order Fermi acceleration, $\dot{p} \sim \Delta p/\tau \sim p\,\langle k c \rangle_{\mathcal{W}} (\delta \varv_{\rm c}/c)^{2}$, where $\tau^{-1} \sim \langle k c \rangle_{\mathcal{W}}$ is the energy averaged wave-particle interaction rate, and $\Delta p \sim p (\delta \varv_{\rm c}/c)^{2}$ is the typical momentum change during wave particle scattering. Thus: 
\begin{equation}
D_{pp} \sim p \dot{p} \sim p^{2} \langle k c \rangle_{\mathcal{W}} \left( \frac{\delta \varv_{\rm c}}{c} \right)^{2}. 
\end{equation}

Equations \ref{eqn:diffusion} and \ref{eqn:Wk} make the important aspects of turbulence clear: the energy in compressive modes $\langle (\delta v_{\rm c})^{2} \rangle$, the inner and outer scale ($k_{\rm cut}$ and $k_{\rm L}$), and the slope of the energy spectrum $s$. All of these can vary spatially and temporally.

{\bf Energy in compressive modes} The total turbulence energy is typically $\sim 15-70\%$ of the thermal energy in a cluster \citep{vazza11}; it rises rapidly during a merger. The compressible component is $\sim 20-40\%$ of the total turbulent energy, and shows more rapid temporal variations compared to the compressible component \citep{2013ApJ...771..131B,2015ApJ...800...60M}. It is worth noting that in the subsonic regime of the solar wind \citep{yao11,howes12}, as well as most idealized calculations of turbulent driving, there is relatively little energy in the fast mode. For instance, the fidiucial simulations of \citet{lynn14} with a sonic Mach number ${\mathcal M}_{\rm s} \sim 0.35$ and a plasma beta factor of $\beta \sim 1$ show that 50\%, 45\%, 5\% of the turbulent energy density is in the Alfv{\'e}n, slow, and fast modes, respectively. For higher $\beta \sim 3-10$, they find that the proportion of energy in fast modes drops to $< 1\%$, while the fraction of energy in the slow mode remains roughly the same. Similarly, \citet{kowal10} find that the fast mode is highly subdominant (see their Table 2); for the run most relevant to cluster conditions ${\mathcal M}_{\rm s} \sim 0.7, \beta \sim 10$, they find $\sim 42\%, 6\%$ of turbulent energy in slow and fast modes respectively. These simulations are roughly consistent with theoretical estimates of $U_{\rm fast}/U_{\rm slow} \sim {\mathcal M}_{\rm s}^{2}/{\mathcal M}_{\rm A}$ \citep{cho03}. By contrast, MHD simulations of galaxy clusters find a large fraction ($\sim 25$\%) of turbulent energy in fast modes \citep{2013ApJ...771..131B}. This is likely due to the compressive nature of turbulent driving (transonic infall and merger), whereas idealized simulations tend to use incompressible solenoidal driving and allow compressive fluctuations to develop on their own.

In the high-$\beta$, subsonic conditions of the ICM, the Alfv{\'e}n/slow modes are exactly/approximately incompressible, and so the approximate identification of compressive modes with fast modes is valid. We therefore take $\sim 25\%$ of the turbulent energy density in compressive fast modes as a reasonable baseline estimate \citep{2013ApJ...771..131B,2015ApJ...800...60M}. If a large fraction of energy is in slow modes, then resonant broadening of wave-particle interactions can render slow modes an efficient acceleration mechanism \citep{lynn14}, as we discuss briefly in \S\ref{?}.

{\bf Slope of the energy spectrum $s$.} At large scales, turbulent motions are subsonic (${\mathcal M}_{\rm s} \sim 0.2-0.5$) but super-Alfv{\'e}nic (${\mathcal M}_{\rm A} \sim 5$). Thus, except in the case where motions are transonic and weak shocks become important, motions are fundamentally hydrodynamic and turbulence follows a Kolmogorov ($s=5/3$) spectrum. However, while the turbulent energy density $U_{\rm t} \propto l^{2/3}$ decreases at small scales, the magnetic energy density is scale-independent. Thus, at some scale $l_{\rm A} \sim l_{\rm o} {\mathcal M}_{\rm A}^{-3}$, where $U_{\rm turb} \sim U_{B}$, the magnetic field becomes dynamically important, and turbulence transitions to the MHD regime. Theory \citep{goldreich95,chandran05} and simulations \citep{cho03} show that in the MHD regime, the Alfv{\'e}n and slow modes have a shallower Kraichnan spectrum ($s=3/2$), with relatively little coupling between the incompressible and compressible modes \citep{cho02,cho03} -- though if weak shocks are important, $s=2$ may be more appropriate (see discussion below).

Since the Kraichnan spectrum is critical in what follows, it is worthwhile taking a moment to recount the origin of the spectral slope $s$ and the cascade rate. In the magnetically dominated regime, two counterpropagating wave packets of scale $l$ interact on an Alfv{\'e}n time $\tau_{\rm A}=l/\varv_{\rm A}$, rather than the eddy turnover time $\tau_{\rm edd} = l/\varv_{\rm l}$. 
Since $\tau_{\rm A} \ll \tau_{\rm edd}$, each interaction results in a small velocity change $\delta \varv_{\rm l} \sim \varv_{\rm l} (\tau_{\rm A}/\tau_{\rm edd})$. If these changes behave like a random walk, the cascade time $\tau_{\rm l}$ it takes for an eddy to become non-linear ($\Delta \varv \sim \varv_{\rm l})$ and cascade to smaller scales is $\varv_{\rm l} \sim \delta \varv_{\rm l} (\tau_{\rm l}/\tau_{\rm A})^{1/2} \sim \varv_{\rm l} \tau_{\rm A}/\tau_{\rm edd} (\tau_{\rm l}/\tau_{\rm A})^{1/2}$, which we can solve to obtain the cascade time: 
\begin{equation}
\tau_{\rm l} \sim \left(\frac{\tau_{\rm edd}}{\tau_{\rm A}}\right)^{2} \tau_{\rm A} \sim \frac{l \varv_{\rm A}}{\varv_{\rm l}^{2}} 
\end{equation}
where we have implicitly assumed isotropy. This implies a dissipation rate $\epsilon \sim \varv_{\rm l}^{2}/\tau_{\rm l} \sim \varv_{\rm l}^{4}/(l \varv_{\rm A})$, or $\varv_{\rm l} \sim (\epsilon l \varv_{A})^{1/4}$. Thus, since $k E(k)\sim \varv_{\rm l}^{2}$, this gives a kinetic energy spectrum: 
\begin{equation}
E(k) \sim (\epsilon \varv_{\rm A})^{1/2} k^{-3/2}.
\end{equation}

Finally, if turbulence is transonic ($M_{\rm s} \sim {\mathcal O}(1)$), then compressible modes can dissipate in weak shocks, as seen in decompositions of the velocity field into solenoidal/compressible components both in idealized simulations \citep{kowal10,porter15}, and cosmological hydrodynamic simulations \citep{2015ApJ...800...60M}. The compressible component has a steep Burgers ($s=2$) spectrum. Burgers turbulence is distinct from other forms of turbulence in that it violates locality in k-space--i.e., power does not gradually cascade, but instead can directly jump from large to small scales via a network of weak shocks. Since the Fourier transform of a step function goes as $k^{-1}$, Burgers turbulence has a power spectrum of $P(k) \propto k^{-2}$. If we contrast the different velocity scalings: $\varv \propto l^{1/4}$ (Kraichnan), $\varv \propto l^{1/3}$ (Kolmogorov), $\varv \propto l^{1/2}$ (Burgers), we see that because of its dissipative nature, Burgers turbulence is the least efficient at transferring energy towards the small scales needed (since the wave particle interaction rate scales as $k$) for efficient acceleration. If Burgers turbulence dominates, then particle acceleration rates are too slow in the face of cooling processes to explain radio halos \citep{2015ApJ...800...60M}.

Given the lack of consensus on the fast mode spectrum, and the fact that turbulent reacceleration is not a viable explanation for radio halos if the spectrum is Burgers-like, we assume a Kraichnan spectrum.

{\bf Inner and outer scale}

{\bf Timescales}

{\bf Scaling solutions} Since the diffusion time is independent of energy (the so-call 'hard sphere' approximation), analytic solutions are possible. The steady state solution is a power-law with a cutoff above a characteristic momentum $p_{\rm eq}$, defined by $t_{\rm acc} \equiv t_{\rm cool} (p_{\rm eq})$ \citep{stawarz08}: 
\begin{equation}
n(p) \propto \left \{
\begin{array}{ll}
p^{-\sigma} & \quad \text{for} \quad p \ll p_{\text{eq}} \, , \\
p^2 {\rm e}^{-p/p_{\text{eq}}} & \quad \text{for} \quad p \sim p_{\text{eq}} \,.
\end{array}
\right.
\end{equation}
%
where $-\sigma = 1/2 - \sqrt{9/4 +
  t_\text{acc}/t_\text{esc}}$ asymptotically approaches $-1$
as $t_\text{acc}/t_\text{esc} \rightarrow 0$.

%%%Fast modes can become more important in highly supersonic turbulence, but this is not relevant to clusters. The magnetic energy density in fast modes scales as $\delta B^{2}_{\rm F} \sim \rho \delta v_{\rm F}^{2}/\beta$ (since magnetic restoring forces

\subsection{Formalism for turbulent reacceleration}
\label{sec:reacc}

We incorporate momentum diffusion for electrons and protons via the
transit-time-damping (TTD) resonance with compressible MHD turbulence,
to model Fermi-II reacceleration \citep{brunetti07,brunetti11}. The
TTD resonance requires the wave frequency to obey the resonance
condition, $\omega=k_\parallel\varv_\parallel$, where $k_\parallel$
and $\varv_\parallel$ are the parallel (projected along the magnetic
field) wavenumber and particle velocity, respectively. This implies
that the particle transit time across the confining wave region
matches the wave period,
$\lambda_{\parallel}/\varv_{\parallel}=\tau_{\rmn{wave}}$. Note, the CRs'
gyroradius does not enter the resonance condition. Hence the CRs that
are in resonance with compressible waves experience Fermi-II
acceleration irrespectively of the length scale of the perturbation.

@@

Provided dissipation of turbulence in the ICM is collisionless,
turbulent cascades of compressible modes become suppressed when
thermal and relativistic particles resonantly interact with
magnetosonic waves via TTD on a timescale $\Gamma^{-1}$ that
approaches the cascading timescale given by $\tau_{kk} \approx
k^2/D_{kk}$. Thus, the cascade is suppressed for wave numbers above
\begin{equation}
\label{eq:kc}
  k_\rmn{cut} \approx \frac{81}{14} \frac{I_0}{\rho \langle \Vph \rangle}
  \left(\frac{\langle\sum_i \Gamma_i(k,\theta)\rangle}{k}\right)^{-2}\,,
\end{equation}
where $2\upi/k_\rmn{cut}\sim 0.1-1$~kpc in the ICM. This constitutes an
effective mean free path for CRs, unless plasma instabilities can
mediate interactions between turbulence and particles on smaller
scales \citep{brunetti11}.
